Make any stupid plot you want

### 2021-02-28 draft/sections/math.tex
must stop touching the data + graphics figures

\begin{figure}[H]
    \includegraphics[width=.5\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the connectivity of the data space, for example if the data is independent points or on a plane or a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

\begin{figure}[H]
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    \caption{The base space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers.}
    \label{fig:base_space_div}
\end{figure}

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_line} the total space \dtotal\ is discrete over points $\dbasepoint \in \dbase$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_plane} \dtotal\ lies over the continuous interval \dbase, meaning the records in the fiber are sampled from a continuous space.} 
    \label{fig:base_example}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=1\textwidth]{figures/math/k_different_types.png}
    \caption{The topological base space \dbase\ encodes the connectivity of the data space, for example if the data is independent points or on a plane or a sphere}
    \label{fig:base_space_types}
\end{figure}
As illustrated in figure~\ref{fig:base_space_types}, \dbase\ is akin to an indexing space into \dtotal\ that describes the structure of \dtotal.  \dbase\ can have any number of dimensions and can be continuous or discrete.

\begin{figure}[H]
    \includegraphics[width=\linewidth]{figures/math/k_qspace.png}
    \caption{The base space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers.}
    \label{fig:base_space_div}
\end{figure}

Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}. In figure~\ref{fig:base_space_div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. 
As with fibers and monoids, we can decompose the total space into components $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
which is a decomposition of \dfiber. The \dbase\ remains the same because the connectivity of records does not change just because there are fewer elements in each record.
\begin{figure}[ht!]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        \caption{}
        \label{fig:base_example_discrete}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \caption{}
        \label{fig:base_example_continuous}
    \end{subfigure}
    \caption{These two datasets have the same (time, temperature) fiber. In figure~\ref{fig:base_example_discrete} the total space \dtotal\ is discrete over points $\dbasepoint \in \dbase$, meaning the records in the fiber are also discrete. In figure~\ref{fig:base_example_continuous} \dtotal\ lies over the continuous interval \dbase, meaning the records in the fiber are sampled from a continuous space.} 
    \label{fig:base_example}
\end{figure}
